---
title: "Gaussian_Process_Code"
author: "Chiwan Kim"
date: "2/3/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# In order to change to calls -> change the testing and training index numbers, change blackscholes formula (-1,1), change total_puts to total_calls
```

##Part 1: Standard Gaussian Process

1-1: Fitting

```{r Fitting_SGP, warning = FALSE}
library(rstan)
source("gp.utility.R")

# Fitting GP model
stan_dat <- read_rdump('Financial_Data_Put_American.R')
fit_gp_SGP_American <- stan(file="gp-fit-6dimension_withBS_SGP.stan", data=stan_dat,
               iter=100, chains=1);
print(fit_gp_SGP_American, pars = c('theta','sigma2','gamma2'))
sum_gp_SGP_American <- extract(fit_gp_SGP_American,permuted=FALSE)
```

```{r Computing Means for prediction_SGP}
# Predicting from GP model
post_mean_theta_1_SGP <- mean(sum_gp_SGP_American[,1,1]) #theta
post_mean_theta_2_SGP <- mean(sum_gp_SGP_American[,1,2]) #theta
post_mean_theta_3_SGP <- mean(sum_gp_SGP_American[,1,3]) #theta
post_mean_theta_4_SGP <- mean(sum_gp_SGP_American[,1,4]) #theta
post_mean_theta_5_SGP <- mean(sum_gp_SGP_American[,1,5]) #theta
post_mean_theta_6_SGP <- mean(sum_gp_SGP_American[,1,6]) #theta
post_mean_sigma2_SGP <- mean(sum_gp_SGP_American[,1,7]) #sigma2
post_mean_gamma2_SGP <- mean(sum_gp_SGP_American[,1,8]) #gamma2
# post_mean_mu_SGP <- stan_dat$blackscholes
post_mean_mu_SGP <- mean(sum_gp_SGP_American[,1,9])


```

```{r Blackscholes and assigning test data-1}
test_start <- 323 #06/10 Puts
test_end <- 559 #06/14 Puts

# test_start <- 560 #06/17 Puts
# test_end <- 852 #06/20 Puts

# test_start <- 609 #06/10 Calls
# test_end <- 999 #06/14 Calls

# test_start <- 433 #06/17 Calls
# test_end <- 700 #06/20 Calls

x2_bs <- cbind(as.numeric(stan_dat$total_puts_American$forward_price[test_start:test_end]),as.numeric(stan_dat$total_puts_American$strike_price[test_start:test_end]),as.numeric(stan_dat$total_puts_American$impl_volatility[test_start:test_end]),as.numeric(stan_dat$total_puts_American$time_to_exp[test_start:test_end]),x.grid_5 <- as.numeric(stan_dat$total_puts_American$dividend_yield[test_start:test_end]),as.numeric(stan_dat$total_puts_American$interest_rate[test_start:test_end]))


library('qrmtools')
library('ragtop')
blackscholes_test <- rep(NA,length(x2_bs[,1]))
for (row in 1:nrow(data.frame(x2_bs))){
  blackscholes_test[row] <- as.numeric(blackscholes(-1,S0=as.numeric(stan_dat$total_puts_American$forward_price[test_start:test_end])[row],K=as.numeric(stan_dat$total_puts_American$strike_price[test_start:test_end])[row],r=as.numeric(stan_dat$total_puts_American$interest_rate[test_start:test_end])[row],t=as.numeric(stan_dat$total_puts_American$time_to_exp[test_start:test_end])[row],vola=as.numeric(stan_dat$total_puts_American$impl_volatility[test_start:test_end])[row],divrate=as.numeric(stan_dat$total_puts_American$dividend_yield[test_start:test_end])[row])$Price)
}

x_1 <- as.numeric(stan_dat$total_puts_American$forward_price_scaled[test_start:test_end])
x_2 <- as.numeric(stan_dat$total_puts_American$strike_price_scaled[test_start:test_end])
x_3 <- as.numeric(stan_dat$total_puts_American$impl_volatility[test_start:test_end])
x_4 <- as.numeric(stan_dat$total_puts_American$time_to_exp_scaled[test_start:test_end])
x_5 <- as.numeric(stan_dat$total_puts_American$dividend_yield[test_start:test_end])
x_6 <- as.numeric(stan_dat$total_puts_American$interest_rate[test_start:test_end])
x2 <- cbind(x_1,x_2,x_3,x_4,x_5,x_6)
# x2 <- x2_bs
```

1-2: Predictions

```{r Predictions_SGP}

post_data_SGP_American <- list(theta=c(post_mean_theta_1_SGP,post_mean_theta_2_SGP,post_mean_theta_3_SGP,post_mean_theta_4_SGP,post_mean_theta_5_SGP,post_mean_theta_6_SGP),sigma2=post_mean_sigma2_SGP,gamma2=post_mean_gamma2_SGP,mu=post_mean_mu_SGP,x_train=stan_dat$x,y1=stan_dat$y,x_test=x2,N1=length(stan_dat$x[,1]),N2=length(x2[,1]), bs = blackscholes_test,variables = 6)
# post_data

pred_gp_SGP <- stan(file="Predictive GP_6dimension_withBS_SGP.stan", data=post_data_SGP_American,iter=200, warmup=0, chains=1, seed=5838298, refresh=100, algorithm = 'Fixed_param')
```

##Part2:  Bdrycov Gaussian Process

2-1: Fitting

```{r Fitting_Bdrycov,warning = FALSE}
# Fitting GP model for Bdrycov
fit_gp_Bdrycov_American <- stan(file="gp-fit-6dimension_withBS_Bdrycov_revised.stan", data=stan_dat,
               iter=100, chains=1);
print(fit_gp_Bdrycov_American, pars = c('theta','sigma2','gamma2'))
sum_gp_Bdrycov_American <- extract(fit_gp_Bdrycov_American,permuted=FALSE)
# saveRDS(fit_gp,file ="fit_gp_vol50_within50spot_7to19days")
```

```{r Computing means for prediction_Bdrycov}
# Predicting from GP model - 2 dimensional case
post_mean_theta_1_Bdrycov <- mean(sum_gp_Bdrycov_American[,1,1]) #theta
post_mean_theta_2_Bdrycov <- mean(sum_gp_Bdrycov_American[,1,2]) #theta
post_mean_theta_3_Bdrycov <- mean(sum_gp_Bdrycov_American[,1,3]) #theta
post_mean_theta_4_Bdrycov <- mean(sum_gp_Bdrycov_American[,1,4]) #theta
post_mean_theta_5_Bdrycov <- mean(sum_gp_Bdrycov_American[,1,5]) #theta
post_mean_theta_6_Bdrycov <- mean(sum_gp_Bdrycov_American[,1,6]) #theta
post_mean_sigma2_Bdrycov <- mean(sum_gp_Bdrycov_American[,1,7]) #sigma2
post_mean_gamma2_Bdrycov <- mean(sum_gp_Bdrycov_American[,1,8]) #gamma2
post_mean_mu_Bdrycov <- stan_dat$blackscholes

```

2-2: Predictions

```{r Predictions_Bdrycov}
# X.grid <- expand.grid(x1 = x.grid_1, x2 = x.grid_2)

post_data_Bdrycov_American <- list(theta=c(post_mean_theta_1_Bdrycov,post_mean_theta_2_Bdrycov,post_mean_theta_3_Bdrycov,post_mean_theta_4_Bdrycov,post_mean_theta_5_Bdrycov,post_mean_theta_6_Bdrycov),sigma2=post_mean_sigma2_Bdrycov,gamma2=post_mean_gamma2_Bdrycov,mu=post_mean_mu_Bdrycov,x_train=stan_dat$x,y1=stan_dat$y,x_test=x2,N1=length(stan_dat$x[,1]),N2=length(x2[,1]), bs = blackscholes_test,variables = 6)
# post_data

pred_gp_Bdrycov <- stan(file="Predictive GP_6dimension_withBS_Bdrycov_revised.stan", data=post_data_Bdrycov_American,iter=200, warmup=0, chains=1, seed=5838298, refresh=100, algorithm = 'Fixed_param')
```

##Part 3 Predictions Versus Truth

3-1: Computing Means Standard GP

```{r Mean & SD of Predictions_SGP}
#Computing Mean
y_predict_values_SGP <- extract(pred_gp_SGP,permuted=FALSE)
y_mean_values_SGP <- c(colMeans(y_predict_values_SGP))
y_mean_values_SGP <- y_mean_values_SGP[1:(length(y_mean_values_SGP)-1)]

#Computing Standard Deviation
pred_gp_summary_SGP <- summary(pred_gp_SGP, sd=c("sd"))$summary
pred_gp_sd_SGP <- pred_gp_summary_SGP[, c("sd")]
y_sd_values_SGP <- pred_gp_sd_SGP[1:(length(pred_gp_sd_SGP)-1)]
```

3-2: Computing Means Bdrycov

```{r Mean & SD of Predictions_Bdrycov}
#Computing Mean
y_predict_values_Bdrycov <- extract(pred_gp_Bdrycov,permuted=FALSE)
y_mean_values_Bdrycov <- c(colMeans(y_predict_values_Bdrycov))
y_mean_values_Bdrycov <- y_mean_values_Bdrycov[1:(length(y_mean_values_Bdrycov)-1)]

#Computing Standard Deviation
pred_gp_summary_Bdrycov <- summary(pred_gp_Bdrycov, sd=c("sd"))$summary
pred_gp_sd_Bdrycov <- pred_gp_summary_Bdrycov[, c("sd")]
y_sd_values_Bdrycov <- pred_gp_sd_Bdrycov[1:(length(pred_gp_sd_Bdrycov)-1)]
```

3-3: Plotting Predicted Values against Truth

```{r prediction accuracy}
par(mfrow=c(1,3))
#Plotting Standard GP
plot(log(y_mean_values_SGP),log(stan_dat$total_puts_American$mid_price[test_start:test_end]),xlim = c(min(log(y_mean_values_SGP),na.rm = TRUE), max(log(y_mean_values_SGP),na.rm = TRUE)),ylim = c(min(log(stan_dat$total_puts_American$mid_price[test_start:test_end])), max(log(stan_dat$total_puts_American$mid_price[test_start:test_end])))) 
abline(0,1)

#Plotting BDrycov
plot(log(y_mean_values_Bdrycov),log(stan_dat$total_puts_American$mid_price[test_start:test_end]), xlim = c(min(log(y_mean_values_Bdrycov),na.rm=TRUE), max(log(y_mean_values_Bdrycov),na.rm=TRUE)),ylim = c(min(log(stan_dat$total_puts_American$mid_price[test_start:test_end])), max(log(stan_dat$total_puts_American$mid_price[test_start:test_end]))))
abline(0,1)

#Plotting Blackscholes
plot(log(blackscholes_test),log(stan_dat$total_puts_American$mid_price[test_start:test_end]), xlim = c(min(log(blackscholes_test),na.rm=TRUE), max(log(blackscholes_test),na.rm=TRUE)),ylim = c(min(log(stan_dat$total_puts_American$mid_price[test_start:test_end])), max(log(stan_dat$total_puts_American$mid_price[test_start:test_end]))))
abline(0,1)

#MSE
library('MLmetrics')
MSE(y_mean_values_SGP,stan_dat$total_puts_American$mid_price[test_start:test_end])
MSE(y_mean_values_Bdrycov,stan_dat$total_puts_American$mid_price[test_start:test_end])
MSE(blackscholes_test,stan_dat$total_puts_American$mid_price[test_start:test_end])
```



##Part 4 Visualizations

4-1: Contour Plots of Forward Price & Strike Price

```{r contour plots_forward_strike}
x.grid_1_cont <- as.numeric(stan_dat$total_puts_American$forward_price_scaled[test_start:test_end])
x.grid_2_cont <- as.numeric(stan_dat$total_puts_American$strike_price_scaled[test_start:test_end])

dim1 <- seq(min(x.grid_1_cont),max(x.grid_1_cont),length.out = 25)
dim2 <- seq(min(x.grid_2_cont),max(x.grid_2_cont),length.out = 25)
X.grid <- expand.grid(x1 = dim1, x2 = dim2)

x.grid_3_cont <- as.numeric(rep(mean(stan_dat$total_puts_American$impl_volatility_scaled[test_start:test_end])),nrow(X.grid))
x.grid_4_cont <- as.numeric(rep(mean(stan_dat$total_puts_American$time_to_exp_scaled[test_start:test_end])),nrow(X.grid))
x.grid_5_cont <- as.numeric(rep(mean(stan_dat$total_puts_American$dividend_yield_scaled[test_start:test_end])),nrow(X.grid))
x.grid_6_cont <- as.numeric(rep(mean(stan_dat$total_puts_American$interest_rate_scaled[test_start:test_end])),nrow(X.grid))

x2_cont <- cbind(X.grid,x.grid_3_cont,x.grid_4_cont,x.grid_5_cont,x.grid_6_cont)

x.grid_1_cont_bs <- as.numeric(stan_dat$total_puts_American$forward_price[test_start:test_end])
x.grid_2_cont_bs <- as.numeric(stan_dat$total_puts_American$strike_price[test_start:test_end])
x.grid_3_cont_bs <- as.numeric(rep(mean(stan_dat$total_puts_American$impl_volatility[test_start:test_end])),nrow(X.grid))
x.grid_4_cont_bs <- as.numeric(rep(mean(stan_dat$total_puts_American$time_to_exp[test_start:test_end])),nrow(X.grid))
x.grid_5_cont_bs <- as.numeric(rep(mean(stan_dat$total_puts_American$dividend_yield[test_start:test_end])),nrow(X.grid))
x.grid_6_cont_bs <- as.numeric(rep(mean(stan_dat$total_puts_American$interest_rate[test_start:test_end])),nrow(X.grid))

dim1_bs <- seq(min(x.grid_1_cont_bs),max(x.grid_1_cont_bs),length.out = 25)
dim2_bs <- seq(min(x.grid_2_cont_bs),max(x.grid_2_cont_bs),length.out = 25)
X.grid_bs <- expand.grid(x1 = dim1_bs, x2 = dim2_bs)

x2_cont_bs <- cbind(X.grid_bs,x.grid_3_cont_bs,x.grid_4_cont_bs,x.grid_5_cont_bs,x.grid_6_cont_bs)

blackscholes_test_cont <- rep(NA,length(x2_cont_bs[,1]))
for (row in 1:nrow(data.frame(x2_cont_bs))){
  blackscholes_test_cont[row] <- as.numeric(blackscholes(-1,S0=x2_cont_bs[row,1],K=x2_cont_bs[row,2],r=x2_cont_bs[row,6],t=x2_cont_bs[row,4],vola=x2_cont_bs[row,3],divrate=x2_cont_bs[row,5])$Price)
}

post_data_cont_SGP <- list(theta=c(post_mean_theta_1_SGP,post_mean_theta_2_SGP,post_mean_theta_3_SGP,post_mean_theta_4_SGP,post_mean_theta_5_SGP,post_mean_theta_6_SGP),sigma2=post_mean_sigma2_SGP,gamma2=post_mean_gamma2_SGP,mu=post_mean_mu_SGP,x_train=stan_dat$x,y1=stan_dat$y,x_test=x2_cont,N1=length(stan_dat$x[,1]),N2=nrow(x2_cont), bs = blackscholes_test_cont,variables = 6)

post_data_cont_Bdrycov <- list(theta=c(post_mean_theta_1_Bdrycov,post_mean_theta_2_Bdrycov,post_mean_theta_3_Bdrycov,post_mean_theta_4_Bdrycov,post_mean_theta_5_Bdrycov,post_mean_theta_6_Bdrycov),sigma2=post_mean_sigma2_Bdrycov,gamma2=post_mean_gamma2_Bdrycov,mu=post_mean_mu_Bdrycov,x_train=stan_dat$x,y1=stan_dat$y,x_test=x2_cont,N1=length(stan_dat$x[,1]),N2=nrow(x2_cont), bs = blackscholes_test_cont,variables = 6)


# post_data

pred_gp_cont_SGP <- stan(file="Predictive GP_6dimension_withBS.stan", data=post_data_cont_SGP,iter=200, warmup=0, chains=1, seed=5838298, refresh=100, algorithm = 'Fixed_param')

pred_gp_cont_Bdrycov <- stan(file="Predictive GP_6dimension_withBS_Bdrycov.stan", data=post_data_cont_Bdrycov,iter=200, warmup=0, chains=1, seed=5838298, refresh=100, algorithm = 'Fixed_param')

#Computing Mean
y_predict_values_cont_SGP <- extract(pred_gp_cont_SGP,permuted=FALSE)
y_mean_values_cont_SGP <- c(colMeans(y_predict_values_cont_SGP))
y_mean_values_cont_SGP <- y_mean_values_cont_SGP[1:(length(y_mean_values_cont_SGP)-1)]

#Computing Standard Deviation
pred_gp_summary_cont_SGP <- summary(pred_gp_cont_SGP, sd=c("sd"))$summary
pred_gp_sd_cont_SGP <- pred_gp_summary_cont_SGP[, c("sd")]
y_sd_values_cont_SGP <- pred_gp_sd_cont_SGP[1:(length(pred_gp_sd_cont_SGP)-1)]

par(mfrow = c(1, 2))
#Contour for Predictions aka mean values of predicitons
contour(dim1, dim2, matrix(y_mean_values_cont_SGP, length(dim1), length(dim2)))
points(x2_cont[,1], x2_cont[,2], pch = 19, cex = 0.5, col = "red")
#Contour of Variance
contour(dim1, dim2, matrix(y_sd_values_cont_SGP, length(dim1), length(dim2)))
points(x2_cont[,1], x2_cont[,2], pch = 19, cex = 0.5, col = "red")

#Computing Mean
y_predict_values_cont_Bdrycov <- extract(pred_gp_cont_Bdrycov,permuted=FALSE)
y_mean_values_cont_Bdrycov <- c(colMeans(y_predict_values_cont_Bdrycov))
y_mean_values_cont_Bdrycov <- y_mean_values_cont_Bdrycov[1:(length(y_mean_values_cont_Bdrycov)-1)]

#Computing Standard Deviation
pred_gp_summary_cont_Bdrycov <- summary(pred_gp_cont_Bdrycov, sd=c("sd"))$summary
pred_gp_sd_cont_Bdrycov <- pred_gp_summary_cont_Bdrycov[, c("sd")]
y_sd_values_cont_Bdrycov <- pred_gp_sd_cont_Bdrycov[1:(length(pred_gp_sd_cont_Bdrycov)-1)]

par(mfrow = c(1, 2))
#Contour for Predictions aka mean values of predicitons
contour(dim1, dim2, matrix(y_mean_values_cont_Bdrycov, length(dim1), length(dim2)))
points(x2_cont[,1], x2_cont[,2], pch = 19, cex = 0.5, col = "red")
#Contour of Variance
contour(dim1, dim2, matrix(y_sd_values_cont_Bdrycov, length(dim1), length(dim2)))
points(x2_cont[,1], x2_cont[,2], pch = 19, cex = 0.5, col = "red")
```

4-2: Contour Plots of Implied VOlatility & Time to Expiration

```{r}
x.grid_1_cont <- as.numeric(stan_dat$total_puts_American$impl_volatility_scaled[test_start:test_end])
x.grid_2_cont <- as.numeric(stan_dat$total_puts_American$time_to_exp_scaled[test_start:test_end])

dim1 <- seq(min(x.grid_1_cont),max(x.grid_1_cont),length.out = 25)
dim2 <- seq(min(x.grid_2_cont),max(x.grid_2_cont),length.out = 25)
X.grid <- expand.grid(x1 = dim1, x2 = dim2)

x.grid_3_cont <- as.numeric(rep(mean(stan_dat$total_puts_American$forward_price_scaled[test_start:test_end])),nrow(X.grid))
x.grid_4_cont <- as.numeric(rep(mean(stan_dat$total_puts_American$strike_price_scaled[test_start:test_end])),nrow(X.grid))
x.grid_5_cont <- as.numeric(rep(mean(stan_dat$total_puts_American$dividend_yield_scaled[test_start:test_end])),nrow(X.grid))
x.grid_6_cont <- as.numeric(rep(mean(stan_dat$total_puts_American$interest_rate_scaled[test_start:test_end])),nrow(X.grid))

x2_cont <- cbind(X.grid,x.grid_3_cont,x.grid_4_cont,x.grid_5_cont,x.grid_6_cont)

x.grid_1_cont_bs <- as.numeric(stan_dat$total_puts_American$impl_volatility[test_start:test_end])
x.grid_2_cont_bs <- as.numeric(stan_dat$total_puts_American$time_to_exp[test_start:test_end])
x.grid_3_cont_bs <- as.numeric(rep(mean(stan_dat$total_puts_American$forward_price[test_start:test_end])),nrow(X.grid))
x.grid_4_cont_bs <- as.numeric(rep(mean(stan_dat$total_puts_American$strike_price[test_start:test_end])),nrow(X.grid))
x.grid_5_cont_bs <- as.numeric(rep(mean(stan_dat$total_puts_American$dividend_yield[test_start:test_end])),nrow(X.grid))
x.grid_6_cont_bs <- as.numeric(rep(mean(stan_dat$total_puts_American$interest_rate[test_start:test_end])),nrow(X.grid))

dim1_bs <- seq(min(x.grid_1_cont_bs),max(x.grid_1_cont_bs),length.out = 25)
dim2_bs <- seq(min(x.grid_2_cont_bs),max(x.grid_2_cont_bs),length.out = 25)
X.grid_bs <- expand.grid(x1 = dim1_bs, x2 = dim2_bs)

x2_cont_bs <- cbind(X.grid_bs,x.grid_3_cont_bs,x.grid_4_cont_bs,x.grid_5_cont_bs,x.grid_6_cont_bs)

blackscholes_test_cont <- rep(NA,length(x2_cont_bs[,1]))
for (row in 1:nrow(data.frame(x2_cont_bs))){
  blackscholes_test_cont[row] <- as.numeric(blackscholes(-1,S0=x2_cont_bs[row,3],K=x2_cont_bs[row,4],r=x2_cont_bs[row,6],t=x2_cont_bs[row,2],vola=x2_cont_bs[row,1],divrate=x2_cont_bs[row,5])$Price)
}


post_data_cont_SGP <- list(theta=c(post_mean_theta_1_SGP,post_mean_theta_2_SGP,post_mean_theta_3_SGP,post_mean_theta_4_SGP,post_mean_theta_5_SGP,post_mean_theta_6_SGP),sigma2=post_mean_sigma2_SGP,gamma2=post_mean_gamma2_SGP,mu=post_mean_mu_SGP,x_train=stan_dat$x,y1=stan_dat$y,x_test=x2_cont,N1=length(stan_dat$x[,1]),N2=nrow(x2_cont), bs = blackscholes_test_cont,variables = 6)

post_data_cont_Bdrycov <- list(theta=c(post_mean_theta_1_Bdrycov,post_mean_theta_2_Bdrycov,post_mean_theta_3_Bdrycov,post_mean_theta_4_Bdrycov,post_mean_theta_5_Bdrycov,post_mean_theta_6_Bdrycov),sigma2=post_mean_sigma2_Bdrycov,gamma2=post_mean_gamma2_Bdrycov,mu=post_mean_mu_Bdrycov,x_train=stan_dat$x,y1=stan_dat$y,x_test=x2_cont,N1=length(stan_dat$x[,1]),N2=nrow(x2_cont), bs = blackscholes_test_cont,variables = 6)


# post_data

pred_gp_cont_SGP <- stan(file="Predictive GP_6dimension_withBS.stan", data=post_data_cont_SGP,iter=200, warmup=0, chains=1, seed=5838298, refresh=100, algorithm = 'Fixed_param')

pred_gp_cont_Bdrycov <- stan(file="Predictive GP_6dimension_withBS_Bdrycov.stan", data=post_data_cont_Bdrycov,iter=200, warmup=0, chains=1, seed=5838298, refresh=100, algorithm = 'Fixed_param')

#Computing Mean
y_predict_values_cont_SGP <- extract(pred_gp_cont_SGP,permuted=FALSE)
y_mean_values_cont_SGP <- c(colMeans(y_predict_values_cont_SGP))
y_mean_values_cont_SGP <- y_mean_values_cont_SGP[1:(length(y_mean_values_cont_SGP)-1)]

#Computing Standard Deviation
pred_gp_summary_cont_SGP <- summary(pred_gp_cont_SGP, sd=c("sd"))$summary
pred_gp_sd_cont_SGP <- pred_gp_summary_cont_SGP[, c("sd")]
y_sd_values_cont_SGP <- pred_gp_sd_cont_SGP[1:(length(pred_gp_sd_cont_SGP)-1)]

par(mfrow = c(1, 2))
#Contour for Predictions aka mean values of predicitons
contour(dim1, dim2, matrix(y_mean_values_cont_SGP, length(dim1), length(dim2)))
points(x2_cont[,1], x2_cont[,2], pch = 19, cex = 0.5, col = "red")
#Contour of Variance
contour(dim1, dim2, matrix(y_sd_values_cont_SGP, length(dim1), length(dim2)))
points(x2_cont[,1], x2_cont[,2], pch = 19, cex = 0.5, col = "red")

#Computing Mean
y_predict_values_cont_Bdrycov <- extract(pred_gp_cont_Bdrycov,permuted=FALSE)
y_mean_values_cont_Bdrycov <- c(colMeans(y_predict_values_cont_Bdrycov))
y_mean_values_cont_Bdrycov <- y_mean_values_cont_Bdrycov[1:(length(y_mean_values_cont_Bdrycov)-1)]

#Computing Standard Deviation
pred_gp_summary_cont_Bdrycov <- summary(pred_gp_cont_Bdrycov, sd=c("sd"))$summary
pred_gp_sd_cont_Bdrycov <- pred_gp_summary_cont_Bdrycov[, c("sd")]
y_sd_values_cont_Bdrycov <- pred_gp_sd_cont_Bdrycov[1:(length(pred_gp_sd_cont_Bdrycov)-1)]

par(mfrow = c(1, 2))
#Contour for Predictions aka mean values of predicitons
contour(dim1, dim2, matrix(y_mean_values_cont_Bdrycov, length(dim1), length(dim2)))
points(x2_cont[,1], x2_cont[,2], pch = 19, cex = 0.5, col = "red")
#Contour of Variance
contour(dim1, dim2, matrix(y_sd_values_cont_Bdrycov, length(dim1), length(dim2)))
points(x2_cont[,1], x2_cont[,2], pch = 19, cex = 0.5, col = "red")
```

4-3: Contour Plots of Interest Rate & Dividend Yield

```{r contour plots_rates_time}
x.grid_1_cont <- as.numeric(stan_dat$total_puts_American$dividend_yield_scaled[test_start:test_end])
x.grid_2_cont <- as.numeric(stan_dat$total_puts_American$interest_rate_scaled[test_start:test_end])

dim1 <- seq(min(x.grid_1_cont),max(x.grid_1_cont),length.out = 25)
dim2 <- seq(min(x.grid_2_cont),max(x.grid_2_cont),length.out = 25)
X.grid <- expand.grid(x1 = dim1, x2 = dim2)

x.grid_3_cont <- as.numeric(rep(mean(stan_dat$total_puts_American$impl_volatility_scaled[test_start:test_end])),nrow(X.grid))
x.grid_4_cont <- as.numeric(rep(mean(stan_dat$total_puts_American$time_to_exp_scaled[test_start:test_end])),nrow(X.grid))
x.grid_5_cont <- as.numeric(rep(mean(stan_dat$total_puts_American$forward_price_scaled[test_start:test_end])),nrow(X.grid))
x.grid_6_cont <- as.numeric(rep(mean(stan_dat$total_puts_American$strike_price_scaled[test_start:test_end])),nrow(X.grid))

x2_cont <- cbind(X.grid,x.grid_3_cont,x.grid_4_cont,x.grid_5_cont,x.grid_6_cont)

x.grid_1_cont_bs <- as.numeric(stan_dat$total_puts_American$dividend_yield[test_start:test_end])
x.grid_2_cont_bs <- as.numeric(stan_dat$total_puts_American$interest_rate[test_start:test_end])
x.grid_3_cont_bs <- as.numeric(rep(mean(stan_dat$total_puts_American$impl_volatility[test_start:test_end])),nrow(X.grid))
x.grid_4_cont_bs <- as.numeric(rep(mean(stan_dat$total_puts_American$time_to_exp[test_start:test_end])),nrow(X.grid))
x.grid_5_cont_bs <- as.numeric(rep(mean(stan_dat$total_puts_American$forward_price[test_start:test_end])),nrow(X.grid))
x.grid_6_cont_bs <- as.numeric(rep(mean(stan_dat$total_puts_American$strike_price[test_start:test_end])),nrow(X.grid))

dim1_bs <- seq(min(x.grid_1_cont_bs),max(x.grid_1_cont_bs),length.out = 25)
dim2_bs <- seq(min(x.grid_2_cont_bs),max(x.grid_2_cont_bs),length.out = 25)
X.grid_bs <- expand.grid(x1 = dim1_bs, x2 = dim2_bs)

x2_cont_bs <- cbind(X.grid_bs,x.grid_3_cont_bs,x.grid_4_cont_bs,x.grid_5_cont_bs,x.grid_6_cont_bs)

blackscholes_test_cont <- rep(NA,length(x2_cont_bs[,1]))
for (row in 1:nrow(data.frame(x2_cont_bs))){
  blackscholes_test_cont[row] <- as.numeric(blackscholes(-1,S0=x2_cont_bs[row,5],K=x2_cont_bs[row,6],r=x2_cont_bs[row,2],t=x2_cont_bs[row,4],vola=x2_cont_bs[row,3],divrate=x2_cont_bs[row,1])$Price)
}


post_data_cont_SGP <- list(theta=c(post_mean_theta_1_SGP,post_mean_theta_2_SGP,post_mean_theta_3_SGP,post_mean_theta_4_SGP,post_mean_theta_5_SGP,post_mean_theta_6_SGP),sigma2=post_mean_sigma2_SGP,gamma2=post_mean_gamma2_SGP,mu=post_mean_mu_SGP,x_train=stan_dat$x,y1=stan_dat$y,x_test=x2_cont,N1=length(stan_dat$x[,1]),N2=nrow(x2_cont), bs = blackscholes_test_cont,variables = 6)

post_data_cont_Bdrycov <- list(theta=c(post_mean_theta_1_Bdrycov,post_mean_theta_2_Bdrycov,post_mean_theta_3_Bdrycov,post_mean_theta_4_Bdrycov,post_mean_theta_5_Bdrycov,post_mean_theta_6_Bdrycov),sigma2=post_mean_sigma2_Bdrycov,gamma2=post_mean_gamma2_Bdrycov,mu=post_mean_mu_Bdrycov,x_train=stan_dat$x,y1=stan_dat$y,x_test=x2_cont,N1=length(stan_dat$x[,1]),N2=nrow(x2_cont), bs = blackscholes_test_cont,variables = 6)


# post_data

pred_gp_cont_SGP <- stan(file="Predictive GP_6dimension_withBS.stan", data=post_data_cont_SGP,iter=200, warmup=0, chains=1, seed=5838298, refresh=100, algorithm = 'Fixed_param')

pred_gp_cont_Bdrycov <- stan(file="Predictive GP_6dimension_withBS_Bdrycov.stan", data=post_data_cont_Bdrycov,iter=200, warmup=0, chains=1, seed=5838298, refresh=100, algorithm = 'Fixed_param')

#Computing Mean
y_predict_values_cont_SGP <- extract(pred_gp_cont_SGP,permuted=FALSE)
y_mean_values_cont_SGP <- c(colMeans(y_predict_values_cont_SGP))
y_mean_values_cont_SGP <- y_mean_values_cont_SGP[1:(length(y_mean_values_cont_SGP)-1)]

#Computing Standard Deviation
pred_gp_summary_cont_SGP <- summary(pred_gp_cont_SGP, sd=c("sd"))$summary
pred_gp_sd_cont_SGP <- pred_gp_summary_cont_SGP[, c("sd")]
y_sd_values_cont_SGP <- pred_gp_sd_cont_SGP[1:(length(pred_gp_sd_cont_SGP)-1)]

par(mfrow = c(1, 2))
#Contour for Predictions aka mean values of predicitons
contour(dim1, dim2, matrix(y_mean_values_cont_SGP, length(dim1), length(dim2)))
points(x2_cont[,1], x2_cont[,2], pch = 19, cex = 0.5, col = "red")
#Contour of Variance
contour(dim1, dim2, matrix(y_sd_values_cont_SGP, length(dim1), length(dim2)))
points(x2_cont[,1], x2_cont[,2], pch = 19, cex = 0.5, col = "red")

#Computing Mean
y_predict_values_cont_Bdrycov <- extract(pred_gp_cont_Bdrycov,permuted=FALSE)
y_mean_values_cont_Bdrycov <- c(colMeans(y_predict_values_cont_Bdrycov))
y_mean_values_cont_Bdrycov <- y_mean_values_cont_Bdrycov[1:(length(y_mean_values_cont_Bdrycov)-1)]

#Computing Standard Deviation
pred_gp_summary_cont_Bdrycov <- summary(pred_gp_cont_Bdrycov, sd=c("sd"))$summary
pred_gp_sd_cont_Bdrycov <- pred_gp_summary_cont_Bdrycov[, c("sd")]
y_sd_values_cont_Bdrycov <- pred_gp_sd_cont_Bdrycov[1:(length(pred_gp_sd_cont_Bdrycov)-1)]

par(mfrow = c(1, 2))
#Contour for Predictions aka mean values of predicitons
contour(dim1, dim2, matrix(y_mean_values_cont_Bdrycov, length(dim1), length(dim2)))
points(x2_cont[,1], x2_cont[,2], pch = 19, cex = 0.5, col = "red")
#Contour of Variance
contour(dim1, dim2, matrix(y_sd_values_cont_Bdrycov, length(dim1), length(dim2)))
points(x2_cont[,1], x2_cont[,2], pch = 19, cex = 0.5, col = "red")
```

##Part 5: Improving the model by incorporating discrepancy

5-1: Computing Predicted European Option Prices

```{r Fitting_SGP_European_discrepancy-1,warning = FALSE}
# Fitting GP model
stan_dat_European <- read_rdump('Financial_Data_Call_European.R')
fit_gp_SGP_European <- stan(file="gp-fit-6dimension_withBS.stan", data=stan_dat_European,
               iter=100, chains=1);
print(fit_gp_SGP_European, pars = c('theta','sigma2','gamma2'))
sum_gp_SGP_European <- extract(fit_gp_SGP_European,permuted=FALSE)
```

```{r Computing Means for prediction_SGP_European_discrepancy-1}
# Predicting from GP model
post_mean_theta_1_SGP <- mean(sum_gp_SGP_European[,1,1]) #theta
post_mean_theta_2_SGP <- mean(sum_gp_SGP_European[,1,2]) #theta
post_mean_theta_3_SGP <- mean(sum_gp_SGP_European[,1,3]) #theta
post_mean_theta_4_SGP <- mean(sum_gp_SGP_European[,1,4]) #theta
post_mean_theta_5_SGP <- mean(sum_gp_SGP_European[,1,5]) #theta
post_mean_theta_6_SGP <- mean(sum_gp_SGP_European[,1,6]) #theta
post_mean_sigma2_SGP <- mean(sum_gp_SGP_European[,1,7]) #sigma2
post_mean_gamma2_SGP <- mean(sum_gp_SGP_European[,1,8]) #gamma2
post_mean_mu_SGP <- stan_dat_European$blackscholes



```

```{r Blackscholes and assigning test data -2}
x2_bs <- cbind(as.numeric(stan_dat$total_puts_American$forward_price[test_start:test_end]),as.numeric(stan_dat$total_puts_American$strike_price[test_start:test_end]),as.numeric(stan_dat$total_puts_American$impl_volatility[test_start:test_end]),as.numeric(stan_dat$total_puts_American$time_to_exp[test_start:test_end]),x.grid_5 <- as.numeric(stan_dat$total_puts_American$dividend_yield[test_start:test_end]),as.numeric(stan_dat$total_puts_American$interest_rate[test_start:test_end]))

blackscholes_test <- rep(NA,length(x2_bs[,1]))
for (row in 1:nrow(data.frame(x2_bs))){
  blackscholes_test[row] <- as.numeric(blackscholes(-1,S0=as.numeric(stan_dat$total_puts_American$forward_price[test_start:test_end])[row],K=as.numeric(stan_dat$total_puts_American$strike_price[test_start:test_end])[row],r=as.numeric(stan_dat$total_puts_American$interest_rate[test_start:test_end])[row],t=as.numeric(stan_dat$total_puts_American$time_to_exp[test_start:test_end])[row],vola=as.numeric(stan_dat$total_puts_American$impl_volatility[test_start:test_end])[row],divrate=as.numeric(stan_dat$total_puts_American$dividend_yield[test_start:test_end])[row])$Price)
}

x.grid_1 <- as.numeric(stan_dat$total_puts_American$forward_price_scaled[test_start:test_end])
x.grid_2 <- as.numeric(stan_dat$total_puts_American$strike_price_scaled[test_start:test_end])
x.grid_3 <- as.numeric(stan_dat$total_puts_American$impl_volatility_scaled[test_start:test_end])
x.grid_4 <- as.numeric(stan_dat$total_puts_American$time_to_exp_scaled[test_start:test_end])
x.grid_5 <- as.numeric(stan_dat$total_puts_American$dividend_yield_scaled[test_start:test_end])
x.grid_6 <- as.numeric(stan_dat$total_puts_American$interest_rate_scaled[test_start:test_end])
x2 <- cbind(x.grid_1,x.grid_2,x.grid_3,x.grid_4,x.grid_5,x.grid_6)

```

```{r Predictions_Bdrycov_discrepancy-1}
# X.grid <- expand.grid(x1 = x.grid_1, x2 = x.grid_2)

post_data_Bdrycov_American_disc <- list(theta=c(post_mean_theta_1_SGP,post_mean_theta_2_SGP,post_mean_theta_3_SGP,post_mean_theta_4_SGP,post_mean_theta_5_SGP,post_mean_theta_6_SGP),sigma2=post_mean_sigma2_SGP,gamma2=post_mean_gamma2_SGP,mu=post_mean_mu_SGP,x_train=stan_dat_European$x,y1=stan_dat_European$y,x_test=x2,N1=length(stan_dat_European$x[,1]),N2=length(x2[,1]), bs = blackscholes_test,variables = 6)
# post_data

pred_gp_Bdrycov_disc <- stan(file="Predictive GP_6dimension_withBS_Bdrycov.stan", data=post_data_Bdrycov_American_disc,iter=200, warmup=0, chains=1, seed=5838298, refresh=100, algorithm = 'Fixed_param')
```

```{r Mean & SD of Predictions_Bdrycov_disc-1}
#Computing Mean
y_predict_values_Bdrycov_disc <- extract(pred_gp_Bdrycov_disc,permuted=FALSE)
y_mean_values_Bdrycov_disc <- c(colMeans(y_predict_values_Bdrycov_disc))
y_mean_values_Bdrycov_disc <- y_mean_values_Bdrycov_disc[1:(length(y_mean_values_Bdrycov_disc)-1)]

#Computing Standard Deviation
pred_gp_summary_Bdrycov_disc <- summary(pred_gp_Bdrycov_disc, sd=c("sd"))$summary
pred_gp_sd_Bdrycov_disc <- pred_gp_summary_Bdrycov_disc[, c("sd")]
y_sd_values_Bdrycov_disc <- pred_gp_sd_Bdrycov_disc[1:(length(pred_gp_sd_Bdrycov_disc)-1)]
```

3-3: Plotting Predicted Values against Truth

```{r prediction accuracy_disc-1}
par(mfrow=c(1,4))
#Plotting Standard GP
plot(log(y_mean_values_SGP),log(stan_dat$total_puts_American$mid_price[test_start:test_end]),xlim = c(min(log(y_mean_values_SGP),na.rm = TRUE), max(log(y_mean_values_SGP),na.rm = TRUE)),ylim = c(min(log(stan_dat$total_puts_American$mid_price[test_start:test_end])), max(log(stan_dat$total_puts_American$mid_price[test_start:test_end])))) 
abline(0,1)

#Plotting BDrycov
plot(log(y_mean_values_Bdrycov),log(stan_dat$total_puts_American$mid_price[test_start:test_end]), xlim = c(min(log(y_mean_values_Bdrycov),na.rm=TRUE), max(log(y_mean_values_Bdrycov),na.rm=TRUE)),ylim = c(min(log(stan_dat$total_puts_American$mid_price[test_start:test_end])), max(log(stan_dat$total_puts_American$mid_price[test_start:test_end]))))
abline(0,1)

#Plotting Blackscholes
plot(log(blackscholes_test),log(stan_dat$total_puts_American$mid_price[test_start:test_end]), xlim = c(min(log(blackscholes_test),na.rm=TRUE), max(log(blackscholes_test),na.rm=TRUE)),ylim = c(min(log(stan_dat$total_puts_American$mid_price[test_start:test_end])), max(log(stan_dat$total_puts_American$mid_price[test_start:test_end]))))
abline(0,1)


#Plotting Discrepancy Model
plot(log(y_mean_values_Bdrycov_disc),log(stan_dat$total_puts_American$mid_price[test_start:test_end]), xlim = c(min(log(y_mean_values_Bdrycov_disc),na.rm=TRUE), max(log(y_mean_values_Bdrycov_disc),na.rm=TRUE)),ylim = c(min(log(stan_dat$total_puts_American$mid_price[test_start:test_end])), max(log(stan_dat$total_puts_American$mid_price[test_start:test_end]))))
abline(0,1)

#MSE
library('MLmetrics')
MSE(y_mean_values_SGP,stan_dat$total_puts_American$mid_price[test_start:test_end])
MSE(y_mean_values_Bdrycov,stan_dat$total_puts_American$mid_price[test_start:test_end])
MSE(blackscholes_test,stan_dat$total_puts_American$mid_price[test_start:test_end])
MSE(y_mean_values_Bdrycov_disc,stan_dat$total_puts_American$mid_price[test_start:test_end])

```
